\chapter{Introduction}


\section{Eye of Opening the Way}

Beneath a fog of insects, beside rolling black waters lapping against dun colored mud, Penóm peaks up above the hot fog on three parallel ridges of Bedrock. Great ocean vessels here exchange their cargo with barges heading up the Turina river bound for Tumíssa or even further upstream. Beholden to Tsolyánu, the Empire of the Petal Throne, the city maintains a veneer of civilization over the rot and moral decay of it's citizens. The emperor may see glowing reports on but the truth is vastly different. The black market here is the principal market and business is mostly by a private greasing of palms to smooth the way. Decay pervades all dimensions of life in Penóm.

In \emph{Blades in Penóm}, you take on the role of \textbf{clan members} struggling to carve out honor and recognition for your clan. Your clan once dominated Penóm, but assassinations and  treachery has reduced your holdings to near bankrupcy. You've taken control from the clan elders, who have died in mysterious circumstance and seek to rebuild your family name into something to fear.

Who knows what really motivates the strange non-humans, demons, or gods and where the source of magic stems from? What's important is in this stew, a savvy band might be able to make just the right opportunities to upset the apple cart and bring honor to your ancestors.

\subsection{The World}

Tékumel is a high fantasy role play setting created by M.A.R. Barker. It's history and setting span a rough 25,000 years and before that was the Time of Darkness.  The world of Tekumel was once a great hub of intergalactic trade. For reasons unknown, it's solar system was ripped from normal space time and it spins alone in a bubble universe. Some think it was hostile action, and others think it was overuse of faster than light travel. The ensuing chaos resulted in a long Time of Darkness, as Tékumel is a world poor in heavy metals and other resources necessary to sustain an advanced technological society. The thin nature of the fabric of reality in this pocket universe allows for magic, direct manipulation by nearby \emph{n}-dimensional beings "demons", and other singular powerful extra-dimensional beings "gods".

Tékumel has layers upon layers of collapsed civilizations from technologically advanced societies to alien, all built upon the ruins of the previous. What lies beneath it all is still unknown.


\subsection{What is this Game About?}

\begin{itemize}
\item Coming together to work as a team, building alliances, negociating deals to bring honor to your clan.
\item Hosting noble dinner parties while simulataneously using subterfuge and thievery to advance your mission.
\item Understanding the web that makes a city function.
\item Taking back power from a corrupt elite. Putting fear into those who stand in your way.
\end{itemize}

\subsubsection{Dramatic Questions}

\begin{itemize}
\item If noone ever finds out, is an action ignoble?
\item How does one maintain civility and manners while secretely at war?
\item It's easy to destroy, but what does it take to build?
\end{itemize}

\subsection{The Game}

\emph{Blades in Penóm} is a roleplaying game about a group of daring characters who are family building the reputation of their high clan. We play to find out if the fledgling clan can thrive amidst the teeming threats that surround it.

\subsection{The Players}

Each player creates a character and works with the other players to create the clan to which their characters belong. Each player strives to bring their character to life as an interesting, daring character who reaches boldly beyond their current safety and means.

The players work together with the Game Master to establish the tone and style of the game by making judgment calls about the mechanics, dice, and consequences of actions. The players take responsibility as co-authors of the game with the GM and should agree on the tone and boundaries of what's allowed in play.

Player who are not experienced in the setting of Tékumel should avoid any of the non-human options.

\subsection{The Characters}

The characters attempt to develop their crew by performing scores and contending with threats from their enemies.
 
\subsection{The Clan}

In addition to creating characters, you’ll also create the clan by choosing which type of enterprise you’re interested in exploring.

\subsection{The Game Master (GM)}

The GM establishes the dynamic world around the characters. The GM plays all the non-player characters in the world by giving each one a concrete desire and preferred method of action.

The GM helps organize the conversation of the game so it’s pointed toward the interesting elements of play. The GM isn’t in charge of the story and doesn’t have to plan events ahead of time. They present interesting opportunities to the players, then follow the chain of action and consequences wherever they lead. \textsc{Note:} It's not just the GM's responsibilty to create an engaging narrative for the group. 

\subsection{Playing A Session}

A session of Blades in the Dark is like an episode of a TV show. There are one or two main events, plus maybe some side-story elements, which all fit into an ongoing series. A session of play can last anywhere from two to six hours, depending on the preferences of the group.

During a session, the  works together to choose a score to accomplish, then they make a few dice rolls to jump into the action of the score in progress. The PCs take actions, suffer consequences, and finish the operation (succeed or fail). Then the crew has downtime, during which they recover, pursue side-projects, and indulge their vices. After downtime, the players once again look for a new opportunity or create their own goals and pursuits, and we play to find out what happens next.


\subsection{How to Use this Book}

Players should read up to \textbf{Chapter 8 - Tékumel} for essentials about the setting. For more expanded histories see (https://www.tekumel.com) and any of the numerous publications from M.A.R. Barker. It's important to have a sense of the rules and mechanics, but deep study is not required.

If you play to run the game of \emph{Blades in Penóm} as a GM, one should be familiar with the entire book. In particular one is expected to know \textbf{Chapter 2 - The Rules} and be able to guide the players through the systems and options.


